\documentclass{article}
\usepackage[utf8]{inputenc}

\title{PS5 Holt}
\author{richard.n.holt }
\date{February 2019}

\begin{document}

\maketitle

\section{Analysis of Data}
This data tells me about the times that the History Channel is playing is shows throughout the day for the current day of the week. Honestly, this data was the final attempt of many fruitless attempts to scrape other websites, but it was one that I was able to scrape on my own!

This data could be used to get data on the shows that the History Channel runs each day as a test of several things including what gets run most often, whether certain political biases might be influencing those decisions. It would be interesting to see whether any alternative viewpoints were influencing a network which, for all intents and purposes, is designed to provide historical information. The ability to parse this data will hopefully help me to understand how to parse data related to far more complex television and news lineups.

\section{Analysis API Data}
In this section, I found surprising data that people in the Norman area seem to be tweeting positive things about President Gallogly. Given recent events on campus, this is interesting to note. Maybe there is more online support than I had assumed, or maybe there is a high level of sarcasm on Twitter.

I used several packages, but the most important one that I used was the twittR package. I used several other R packages that I have used in other classes to interpret and analyze the sentiments in the words.

\end{document}
